::: {#Alaska_lifeform_area .sd-page} 
### Region 1 Alaska - Lifeforms by Area 

Across all area that you have treated in this region in your career, what percent of the area's have you applied seeds belonging to this lifeforms to?

```{r Lifeforms by Area - Alaska}
#| column: screen-inset-shaded
#| layout-ncol: 3
#| layout-nrow: 4

# ALL THE LIFEFORM QUESTIONS GO HERE...
sd_question('numeric', paste0('Graminoids', '12-51', 'area'), paste0('51', 'Graminoids'))
sd_question('numeric', paste0('Graminoids', '12-71', 'area'), paste0('71', 'Graminoids'))
sd_question('numeric', paste0('Graminoids', '12-81', 'area'), paste0('81', 'Graminoids'))
sd_question('numeric', paste0('Forbs', '12-51', 'area'), paste0('51', 'Forbs'))
sd_question('numeric', paste0('Forbs', '12-71', 'area'), paste0('71', 'Forbs'))
sd_question('numeric', paste0('Forbs', '12-81', 'area'), paste0('81', 'Forbs'))
sd_question('numeric', paste0('Shrubs', '12-51', 'area'), paste0('51', 'Shrubs'))
sd_question('numeric', paste0('Shrubs', '12-71', 'area'), paste0('71', 'Shrubs'))
sd_question('numeric', paste0('Shrubs', '12-81', 'area'), paste0('81', 'Shrubs'))
sd_question('numeric', paste0('Trees', '12-51', 'area'), paste0('51', 'Trees'))
sd_question('numeric', paste0('Trees', '12-71', 'area'), paste0('71', 'Trees'))
sd_question('numeric', paste0('Trees', '12-81', 'area'), paste0('81', 'Trees'))

```

```{r}
sd_next(next_page = 'Alaska_lifeform_prop')
```
:::

::: {#Alaska_lifeform_prop .sd-page}

### Alaska - Lifeforms by Seed Mix

When using these lifeforms in a restoration what proportion of a seed mix do they make up?

```{r Lifeforms by Seed Mix - Alaska}
#| column: screen-inset-shaded
#| layout-ncol: 3
#| layout-nrow: 4

# ALL THE LIFEFORM PROP QUESTIONS GO HERE...
sd_question('numeric', paste0('Graminoids', '12-51', 'proportion'), paste0('51', 'Graminoids'))
sd_question('numeric', paste0('Graminoids', '12-71', 'proportion'), paste0('71', 'Graminoids'))
sd_question('numeric', paste0('Graminoids', '12-81', 'proportion'), paste0('81', 'Graminoids'))
sd_question('numeric', paste0('Forbs', '12-51', 'proportion'), paste0('51', 'Forbs'))
sd_question('numeric', paste0('Forbs', '12-71', 'proportion'), paste0('71', 'Forbs'))
sd_question('numeric', paste0('Forbs', '12-81', 'proportion'), paste0('81', 'Forbs'))
sd_question('numeric', paste0('Shrubs', '12-51', 'proportion'), paste0('51', 'Shrubs'))
sd_question('numeric', paste0('Shrubs', '12-71', 'proportion'), paste0('71', 'Shrubs'))
sd_question('numeric', paste0('Shrubs', '12-81', 'proportion'), paste0('81', 'Shrubs'))
sd_question('numeric', paste0('Trees', '12-51', 'proportion'), paste0('51', 'Trees'))
sd_question('numeric', paste0('Trees', '12-71', 'proportion'), paste0('71', 'Trees'))
sd_question('numeric', paste0('Trees', '12-81', 'proportion'), paste0('81', 'Trees'))

```

```{r}
sd_next(next_page = 'Alaska_species')
```
:::

::: {#Alaska_species .sd-page}

### Alaska - Common Species

For each of the following species please. DO STUFF
:::: {.column .species-odd width='98%'}

<center>Linnaea borealis</center>

::: {.column .species-numbers width='49%'}

<center>Realized</center>
```{r}
sd_question(type  = 'numeric', id = paste0('Linnaea_borealis', '-', 12, '-realized-area'), label = 'Proportion of Area?')
sd_question(type  = 'numeric', id = paste0('Linnaea_borealis', '-', 12, '-realized-prop'), label = 'Proportion of Seedmix?')
```

:::

::: {.column .species-numbers width='49%'}
<center>Desired</center>
```{r}
sd_question(type  = 'numeric', id = paste0('Linnaea_borealis', '-', 12, '-desired-area'), label = 'Proportion of Area?')
sd_question(type  = 'numeric', id = paste0('Linnaea_borealis', '-', 12, '-desired-prop'), label = 'Proportion of Seedmix?')
```

:::

::::
:::: {.column .species-odd width='98%'}

<center>Pumpkin eater</center>

::: {.column .species-numbers width='49%'}

<center>Realized</center>
```{r}
sd_question(type  = 'numeric', id = paste0('Pumpkin eater', '-', 12, '-realized-area'), label = 'Proportion of Area?')
sd_question(type  = 'numeric', id = paste0('Pumpkin eater', '-', 12, '-realized-prop'), label = 'Proportion of Seedmix?')
```

:::

::: {.column .species-numbers width='49%'}
<center>Desired</center>
```{r}
sd_question(type  = 'numeric', id = paste0('Pumpkin eater', '-', 12, '-desired-area'), label = 'Proportion of Area?')
sd_question(type  = 'numeric', id = paste0('Pumpkin eater', '-', 12, '-desired-prop'), label = 'Proportion of Seedmix?')
```

:::

::::

```{r}
sd_next(next_page = 'end')
```

:::

::: {#end .sd-page}

##End

Thanks for your help, we know the data are a little nebulous, but it is difficult to balance responses with survey length.

```{r}
sd_close('Exit Survey')
```

```
:::
