---
echo: false
warning: false
format:
  html:
    theme: styles.css
barposition: top 
---

```{r}
library(surveydown)
```

::: {#welcome .sd-page}
# Welcome to our survey!
We would like to know a little bit about you so that we only ask questions relevant to your expertise.  

```{r respondent name}
sd_question(
  type  = "text",
  id    = "FirstName",
  label = "What is your first name?"
)

sd_question(
  type  = "text",
  id    = "LastName",
  label = "And your last name?"
)

sd_question(
  type  = "mc_buttons",
  id    = "email_followup",
  label = "Can we follow up with you on any questions we may have regarding the survey?",
    option = c(
    "Yes"   = "Yes",
    "No"   = "No"
  )
)

sd_question(
  type  = "text",
  id    = "respondent_email_address",
  label = "What is your email address?"
)
```

```{r respondent agency}
sd_question(
  type   = 'mc_buttons',
  id     = 'respondentAgency',
  label  = "Which agency do you currently work for?",
  option = c(
    "BIA"   = "BIA",
    "BLM"   = "BLM",
    "NPS"   = "NPS",
    "USFWS" = "USFWS",
    "Other" = "other"
  )
)

sd_question(
  type  = "text",
  id    = "respondentAgency_other", 
  label = "If you selected 'other' above, please specify the agency you work for:"
)
```

The next question will require some information on which DOI region you are in.
If you don't know click the button below to view a map at doi.gov.

```{r DOI region map}
sd_redirect(
  id     = "redirect",
  url    = "https://www.doi.gov/sites/doi.gov/files/uploads/12-unified-regions-based-on-watersheds-17x11-250dpi-20191018.pdf",
  label  = "DOI region",
  button = TRUE,
  newtab = TRUE
)
```

In order to avoid having multiple respondents duplicating information about areas treated we ask that your responses per region 

```{r respondent DOI region}
sd_question(
  type   = 'mc_buttons',
  id     = 'respondent_DOI_region',
  direction = 'vertical', 
  label  = "Which DOI region is your office primarily located in?",
  option = c(
    "1 North Atlantic-Appalachian" = 1,
    "2 South Atlantic-Gulf" = 2,
    "3 Great Lakes" = 3,
    "4 Mississippi Basin" = 4,
    "5 Missouri Basin" = 5,
    "6 Arkansas-Rio Grande-Texas-Gulf" = 6,
    "7 Upper Colorado Basin" = 7,
    "8 Lower Colorado Basin" = 8,
    "9 Columbia-Pacific Northwest" = 9,
    "10 California-Great-Basin" = 9,
    "11 Alaska" = 11,
    "12 Pacific Islands" = 12
  )
)
```

Before heading to your DOI regions survey you may want to take a quick glimpse at the Multi-Resolution Land Characteristics Consortium data set for NLCD... Using the small 'i' button on the upper left of the map you can identify a pixels' class, we'll associate these numbers with their names in the coming pages. 

```{r MRLC link 1}
sd_redirect(
  id     = "redirect",
  url    = "https://www.mrlc.gov/viewer/",
  label  = "https://www.mrlc.gov/viewer/",
  button = TRUE,
  newtab = TRUE
)
```

```{r}
sd_next(label = 'Head to my regions survey')
```

:::


::: {#Alaska_lifeform_area .sd-page}

### Region 11 - Alaska - Lifeforms by Area

```{r}
region <- 12
nlcd <- c(42, 52, 68)
```

Across all area that you have treated in this region in your career, what percent of the area's have you applied seeds belonging to this lifeforms to? 

```{r Lifeforms by Area}
#| column: screen-inset-shaded
#| layout-ncol: 3
#| layout-nrow: 4

sd_question(type  = "numeric", id = paste0("Graminoid", region, '-', nlcd[1], "area"), 
            label = paste0(nlcd[1], "\nGraminoids:"))
sd_question(type  = "numeric", id = paste0("Graminoid", region, '-', nlcd[2], "area"), 
            label = paste0(nlcd[2], "\nGraminoids:"))
sd_question(type  = "numeric", id = paste0("Graminoid", region, '-', nlcd[3], "area"),
            label = paste0(nlcd[3], "\nGraminoids:"))

sd_question(type  = "numeric", id = paste0("Forbs", region, '-', nlcd[1], "area"), label = "Forbs:")
sd_question(type  = "numeric", id = paste0("Forbs", region, '-', nlcd[2], "area"), label = "Forbs:")
sd_question(type  = "numeric", id = paste0("Forbs", region, '-', nlcd[3], "area"), label = "Forbs:")

sd_question(type  = "numeric", id = paste0("Shrubs", region, '-', nlcd[1], "area"), label = "Shrubs:")
sd_question(type  = "numeric", id = paste0("Shrubs", region, '-', nlcd[2], "area"), label = "Shrubs:")
sd_question(type  = "numeric", id = paste0("Shrubs", region, '-', nlcd[3], "area"), label = "Shrubs:")

sd_question(type  = "numeric", id = paste0("Trees", region, '-', nlcd[1], "area"), label = "Trees:")
sd_question(type  = "numeric", id = paste0("Trees", region, '-', nlcd[2], "area"), label = "Trees:")
sd_question(type  = "numeric", id = paste0("Trees", region, '-', nlcd[3], "area"), label = "Trees:")
```

```{r}
sd_next(next_page = 'Alaska_lifeform_prop')
```
:::

::: {#Alaska_lifeform_prop .sd-page} 

### Region 11 - Alaska - Lifeforms by Seed Mix

When using these lifeforms in a restoration what proportion of a seed mix do they make up? 

```{r Lifeforms by Seed Mix}
#| column: screen-inset-shaded
#| layout-ncol: 3
#| layout-nrow: 4

sd_question(type  = "numeric", id = paste0("Graminoid", region, '-', nlcd[1], "area"), 
            label = paste0(nlcd[1], "\nGraminoids:"))
sd_question(type  = "numeric", id = paste0("Graminoid", region, '-', nlcd[2], "area"), 
            label = paste0(nlcd[2], "\nGraminoids:"))
sd_question(type  = "numeric", id = paste0("Graminoid", region, '-', nlcd[3], "area"),
            label = paste0(nlcd[3], "\nGraminoids:"))

sd_question(type  = "numeric", id = paste0("Forbs", region, '-', nlcd[1], "area"), label = "Forbs:")
sd_question(type  = "numeric", id = paste0("Forbs", region, '-', nlcd[2], "area"), label = "Forbs:")
sd_question(type  = "numeric", id = paste0("Forbs", region, '-', nlcd[3], "area"), label = "Forbs:")

sd_question(type  = "numeric", id = paste0("Shrubs", region, '-', nlcd[1], "area"), label = "Shrubs:")
sd_question(type  = "numeric", id = paste0("Shrubs", region, '-', nlcd[2], "area"), label = "Shrubs:")
sd_question(type  = "numeric", id = paste0("Shrubs", region, '-', nlcd[3], "area"), label = "Shrubs:")

sd_question(type  = "numeric", id = paste0("Trees", region, '-', nlcd[1], "area"), label = "Trees:")
sd_question(type  = "numeric", id = paste0("Trees", region, '-', nlcd[2], "area"), label = "Trees:")
sd_question(type  = "numeric", id = paste0("Trees", region, '-', nlcd[3], "area"), label = "Trees:")
```

```{r}
sd_next(next_page = 'Alaska_species')
```
::: 

::: {#Alaska_species .sd-page} 

### Region 11 - Alaska - Species 

When species the species is the EC to the SPP

::: {.column .text-col width="100%"}

```{r}
sd_question(type  = "numeric", id = paste0("Trees", region, '-', nlcd[1], "area"), label = "Trees:")
```

:::

```{r}
sd_next(next_page = 'end')
```

::: 

::: {#end .sd-page}

## End

This it the last page in the survey. Thanks for your help, we know the data are a little nebulous, but it is difficult to balance responses with survey length. 

```{r}
sd_close("Exit Survey")
```

::: 
