---
echo: false
warning: false
format:
 html:
  theme: [flatly, styles.css]
barposition: top
---

```{r}
library(surveydown)
```

::: {#welcome .sd-page}
# Welcome to the survey!

We would like to know a little bit about you so that we only ask questions relevant to your expertise.

```{r respondent name}
sd_question(
  type  = 'text',
  id    = 'FirstName',
  label = 'What is your first name?'
)

sd_question(
  type  = 'text',
  id    = 'LastName'
,  label = 'And your last name?'
)

sd_question(
  type  = 'mc_buttons',
  id    = 'email_followup',
  label = 'Can we follow up with you on any questions we may have regarding the survey?',
  option = c(
    'Yes'   = 'Yes',
    'No'   = 'No'
  )
)

sd_question(
  type  = 'text',
  id    = 'respondent_email_address',
  label = 'What is your email address?'
)
```

```{r respondent agency}
sd_question(
  type   = 'mc_buttons',
  id     = 'respondentAgency',
  label  = 'Which agency do you currently work for?',
  option = c(
    'BIA'   = 'BIA',
    'BLM'   = 'BLM',
    'NPS'   = 'NPS',
   'USFWS' = 'USFWS',
   'Other' = 'other'
  )
)

sd_question(
  type  = 'text',
  id    = 'respondentAgency_other',
  label = 'If you selected Other above, please specify the agency you work for:'
)
```

The next question will require some information on which DOI region you are in.
If you don't know click the button below to view a map at doi.gov.

```{r DOI region map}
sd_redirect(
  id     = 'redirect',
  url    = 'https://www.doi.gov/sites/doi.gov/files/uploads/12-unified-regions-based-on-watersheds-17x11-250dpi-20191018.pdf',
  label  = 'DOI region',
  button = TRUE,
  newtab = TRUE
)
```
In order to avoid having multiple respondents duplicating information about areas treated we ask that your responses per region.

```{r respondent DOI region}
sd_question(
  type   = 'mc_buttons',
  id     = 'respondent_DOI_region',
  direction = 'vertical',
  label  = 'Which DOI region is your office primarily located in?',
  option = c(
   '1 North Atlantic-Appalachian' = 1,
    '2 South Atlantic-Gulf' = 2,
    '3 Great Lakes' = 3,
    '4 Mississippi Basin' = 4,
    '5 Missouri Basin' = 5,
    '6 Arkansas-Rio Grande-Texas-Gulf' = 6,
    '7 Upper Colorado Basin' = 7,
    '8 Lower Colorado Basin' = 8,
    '9 Columbia-Pacific Northwest' = 9,
    '10 California-Great-Basin' = 10,
    '11 Alaska' = 11,
    '12 Pacific Islands' = 12
 )
)
```

Before heading to your DOI regions survey you may want to take a quick glimpse at the Multi-Resolution Land Characteristics Consortium data set for NLCD... Using the small 'i' button on the upper left of the map you can identify a pixels' class, we'll associate these numbers with their names in the coming pages.

```{r MRLC link 1}
sd_redirect(
  id     = 'redirect',
  url    = 'https://www.mrlc.gov/viewer/',
  label  = 'https://www.mrlc.gov/viewer/',
  button = TRUE,
  newtab = TRUE
)
```

```{r}
sd_next(label = 'Head to my regions survey')
```

:::


::: {#Upper_Colorado_Basin_lifeform_area .sd-page}

### Region 1 Upper Colorado Basin - Lifeforms by Area 

Across all area that you have treated in this region in your career, what percent of the area's have you applied seeds belonging to this lifeforms to?

```{r Lifeforms by Area - Upper Colorado Basin}
#| column: screen-inset-shaded
#| layout-ncol: 3
#| layout-nrow: 4

sd_question('numeric', paste0('Graminoids', '7-51', 'area'), paste('51', 'Graminoids'))
sd_question('numeric', paste0('Graminoids', '7-71', 'area'), paste('71', 'Graminoids'))
sd_question('numeric', paste0('Graminoids', '7-81', 'area'), paste('81', 'Graminoids'))
sd_question('numeric', paste0('Forbs', '7-51', 'area'), paste('51', 'Forbs'))
sd_question('numeric', paste0('Forbs', '7-71', 'area'), paste('71', 'Forbs'))
sd_question('numeric', paste0('Forbs', '7-81', 'area'), paste('81', 'Forbs'))
sd_question('numeric', paste0('Shrubs', '7-51', 'area'), paste('51', 'Shrubs'))
sd_question('numeric', paste0('Shrubs', '7-71', 'area'), paste('71', 'Shrubs'))
sd_question('numeric', paste0('Shrubs', '7-81', 'area'), paste('81', 'Shrubs'))
sd_question('numeric', paste0('Trees', '7-51', 'area'), paste('51', 'Trees'))
sd_question('numeric', paste0('Trees', '7-71', 'area'), paste('71', 'Trees'))
sd_question('numeric', paste0('Trees', '7-81', 'area'), paste('81', 'Trees'))

```

```{r}
sd_next(next_page = 'Upper_Colorado_Basin_lifeform_prop')
```
:::

::: {#Upper_Colorado_Basin_lifeform_prop .sd-page}

### Upper Colorado Basin - Lifeforms by Seed Mix

When using these lifeforms in a restoration what proportion of a seed mix do they make up?

```{r Lifeforms by Seed Mix - Upper Colorado Basin}
#| column: screen-inset-shaded
#| layout-ncol: 3
#| layout-nrow: 4

sd_question('numeric', paste0('Graminoids', '7-51', 'proportion'), paste('51', 'Graminoids'))
sd_question('numeric', paste0('Graminoids', '7-71', 'proportion'), paste('71', 'Graminoids'))
sd_question('numeric', paste0('Graminoids', '7-81', 'proportion'), paste('81', 'Graminoids'))
sd_question('numeric', paste0('Forbs', '7-51', 'proportion'), paste('51', 'Forbs'))
sd_question('numeric', paste0('Forbs', '7-71', 'proportion'), paste('71', 'Forbs'))
sd_question('numeric', paste0('Forbs', '7-81', 'proportion'), paste('81', 'Forbs'))
sd_question('numeric', paste0('Shrubs', '7-51', 'proportion'), paste('51', 'Shrubs'))
sd_question('numeric', paste0('Shrubs', '7-71', 'proportion'), paste('71', 'Shrubs'))
sd_question('numeric', paste0('Shrubs', '7-81', 'proportion'), paste('81', 'Shrubs'))
sd_question('numeric', paste0('Trees', '7-51', 'proportion'), paste('51', 'Trees'))
sd_question('numeric', paste0('Trees', '7-71', 'proportion'), paste('71', 'Trees'))
sd_question('numeric', paste0('Trees', '7-81', 'proportion'), paste('81', 'Trees'))

```

```{r}
sd_next(next_page = 'Upper_Colorado_Basin_species')
```
:::

::: {#Upper_Colorado_Basin_species .sd-page}

### Upper Colorado Basin - Common Species

For each of the following species please. DO STUFF

:::: {.column .species-odd width='98%'}

<center>Achnatherum hymneoides</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Achnatherum_hymneoides', '-', 7, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Achnatherum_hymneoides', '-', 7, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Achnatherum_hymneoides', '-', 7, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Achnatherum_hymneoides', '-', 7, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-even width='98%'}

<center>Pascopyrum smithii</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Pascopyrum_smithii', '-', 7, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Pascopyrum_smithii', '-', 7, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Pascopyrum_smithii', '-', 7, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Pascopyrum_smithii', '-', 7, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-odd width='98%'}

<center>Poa secunda</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Poa_secunda', '-', 7, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Poa_secunda', '-', 7, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Poa_secunda', '-', 7, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Poa_secunda', '-', 7, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-even width='98%'}

<center>Elymus elymoides</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Elymus_elymoides', '-', 7, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Elymus_elymoides', '-', 7, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Elymus_elymoides', '-', 7, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Elymus_elymoides', '-', 7, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-odd width='98%'}

<center>Pseudoroegneria spicata</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Pseudoroegneria_spicata', '-', 7, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Pseudoroegneria_spicata', '-', 7, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Pseudoroegneria_spicata', '-', 7, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Pseudoroegneria_spicata', '-', 7, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-even width='98%'}

<center>Sporobolus cryptandrus</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Sporobolus_cryptandrus', '-', 7, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Sporobolus_cryptandrus', '-', 7, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Sporobolus_cryptandrus', '-', 7, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Sporobolus_cryptandrus', '-', 7, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-odd width='98%'}

<center>Elymus lanceolatus</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Elymus_lanceolatus', '-', 7, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Elymus_lanceolatus', '-', 7, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Elymus_lanceolatus', '-', 7, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Elymus_lanceolatus', '-', 7, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-even width='98%'}

<center>Elymus trachycaulus</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Elymus_trachycaulus', '-', 7, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Elymus_trachycaulus', '-', 7, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Elymus_trachycaulus', '-', 7, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Elymus_trachycaulus', '-', 7, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-odd width='98%'}

<center>Bouteloua gracilis</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Bouteloua_gracilis', '-', 7, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Bouteloua_gracilis', '-', 7, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Bouteloua_gracilis', '-', 7, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Bouteloua_gracilis', '-', 7, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-even width='98%'}

<center>Hesperostipa comata</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Hesperostipa_comata', '-', 7, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Hesperostipa_comata', '-', 7, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Hesperostipa_comata', '-', 7, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Hesperostipa_comata', '-', 7, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-odd width='98%'}

<center>Achillea millefolium</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Achillea_millefolium', '-', 7, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Achillea_millefolium', '-', 7, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Achillea_millefolium', '-', 7, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Achillea_millefolium', '-', 7, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-even width='98%'}

<center>Machaeranthera canescens</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Machaeranthera_canescens', '-', 7, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Machaeranthera_canescens', '-', 7, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Machaeranthera_canescens', '-', 7, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Machaeranthera_canescens', '-', 7, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-odd width='98%'}

<center>Heterotheca villosa</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Heterotheca_villosa', '-', 7, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Heterotheca_villosa', '-', 7, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Heterotheca_villosa', '-', 7, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Heterotheca_villosa', '-', 7, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-even width='98%'}

<center>Linum lewisii</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Linum_lewisii', '-', 7, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Linum_lewisii', '-', 7, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Linum_lewisii', '-', 7, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Linum_lewisii', '-', 7, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-odd width='98%'}

<center>Penstemon linarioides</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Penstemon_linarioides', '-', 7, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Penstemon_linarioides', '-', 7, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Penstemon_linarioides', '-', 7, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Penstemon_linarioides', '-', 7, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

```{r}
sd_next(next_page = 'end', label = 'Head to exit')
```

:::


::: {#Great_Lakes_lifeform_area .sd-page}

### Region 2 Great Lakes - Lifeforms by Area 

Across all area that you have treated in this region in your career, what percent of the area's have you applied seeds belonging to this lifeforms to?

```{r Lifeforms by Area - Great Lakes}
#| column: screen-inset-shaded
#| layout-ncol: 3
#| layout-nrow: 4

sd_question('numeric', paste0('Graminoids', '3-12', 'area'), paste('12', 'Graminoids'))
sd_question('numeric', paste0('Graminoids', '3-23', 'area'), paste('23', 'Graminoids'))
sd_question('numeric', paste0('Graminoids', '3-45', 'area'), paste('45', 'Graminoids'))
sd_question('numeric', paste0('Forbs', '3-12', 'area'), paste('12', 'Forbs'))
sd_question('numeric', paste0('Forbs', '3-23', 'area'), paste('23', 'Forbs'))
sd_question('numeric', paste0('Forbs', '3-45', 'area'), paste('45', 'Forbs'))
sd_question('numeric', paste0('Shrubs', '3-12', 'area'), paste('12', 'Shrubs'))
sd_question('numeric', paste0('Shrubs', '3-23', 'area'), paste('23', 'Shrubs'))
sd_question('numeric', paste0('Shrubs', '3-45', 'area'), paste('45', 'Shrubs'))
sd_question('numeric', paste0('Trees', '3-12', 'area'), paste('12', 'Trees'))
sd_question('numeric', paste0('Trees', '3-23', 'area'), paste('23', 'Trees'))
sd_question('numeric', paste0('Trees', '3-45', 'area'), paste('45', 'Trees'))

```

```{r}
sd_next(next_page = 'Great_Lakes_lifeform_prop')
```
:::

::: {#Great_Lakes_lifeform_prop .sd-page}

### Great Lakes - Lifeforms by Seed Mix

When using these lifeforms in a restoration what proportion of a seed mix do they make up?

```{r Lifeforms by Seed Mix - Great Lakes}
#| column: screen-inset-shaded
#| layout-ncol: 3
#| layout-nrow: 4

sd_question('numeric', paste0('Graminoids', '3-12', 'proportion'), paste('12', 'Graminoids'))
sd_question('numeric', paste0('Graminoids', '3-23', 'proportion'), paste('23', 'Graminoids'))
sd_question('numeric', paste0('Graminoids', '3-45', 'proportion'), paste('45', 'Graminoids'))
sd_question('numeric', paste0('Forbs', '3-12', 'proportion'), paste('12', 'Forbs'))
sd_question('numeric', paste0('Forbs', '3-23', 'proportion'), paste('23', 'Forbs'))
sd_question('numeric', paste0('Forbs', '3-45', 'proportion'), paste('45', 'Forbs'))
sd_question('numeric', paste0('Shrubs', '3-12', 'proportion'), paste('12', 'Shrubs'))
sd_question('numeric', paste0('Shrubs', '3-23', 'proportion'), paste('23', 'Shrubs'))
sd_question('numeric', paste0('Shrubs', '3-45', 'proportion'), paste('45', 'Shrubs'))
sd_question('numeric', paste0('Trees', '3-12', 'proportion'), paste('12', 'Trees'))
sd_question('numeric', paste0('Trees', '3-23', 'proportion'), paste('23', 'Trees'))
sd_question('numeric', paste0('Trees', '3-45', 'proportion'), paste('45', 'Trees'))

```

```{r}
sd_next(next_page = 'Great_Lakes_species')
```
:::

::: {#Great_Lakes_species .sd-page}

### Great Lakes - Common Species

For each of the following species please. DO STUFF

:::: {.column .species-odd width='98%'}

<center>Andropogon gerardii</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Andropogon_gerardii', '-', 3, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Andropogon_gerardii', '-', 3, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Andropogon_gerardii', '-', 3, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Andropogon_gerardii', '-', 3, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-even width='98%'}

<center>Schizachyyrium scoparium</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Schizachyyrium_scoparium', '-', 3, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Schizachyyrium_scoparium', '-', 3, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Schizachyyrium_scoparium', '-', 3, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Schizachyyrium_scoparium', '-', 3, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-odd width='98%'}

<center>Bouteloua curtipendula</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Bouteloua_curtipendula', '-', 3, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Bouteloua_curtipendula', '-', 3, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Bouteloua_curtipendula', '-', 3, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Bouteloua_curtipendula', '-', 3, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-even width='98%'}

<center>Sorghastrum nutans</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Sorghastrum_nutans', '-', 3, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Sorghastrum_nutans', '-', 3, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Sorghastrum_nutans', '-', 3, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Sorghastrum_nutans', '-', 3, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-odd width='98%'}

<center>Sporobolus heterolepis</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Sporobolus_heterolepis', '-', 3, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Sporobolus_heterolepis', '-', 3, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Sporobolus_heterolepis', '-', 3, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Sporobolus_heterolepis', '-', 3, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-even width='98%'}

<center>Dalea purpurea</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Dalea_purpurea', '-', 3, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Dalea_purpurea', '-', 3, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Dalea_purpurea', '-', 3, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Dalea_purpurea', '-', 3, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-odd width='98%'}

<center>Eryngium yuccifolium</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Eryngium_yuccifolium', '-', 3, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Eryngium_yuccifolium', '-', 3, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Eryngium_yuccifolium', '-', 3, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Eryngium_yuccifolium', '-', 3, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-even width='98%'}

<center>Mondarda fistulosa</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Mondarda_fistulosa', '-', 3, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Mondarda_fistulosa', '-', 3, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Mondarda_fistulosa', '-', 3, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Mondarda_fistulosa', '-', 3, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-odd width='98%'}

<center>Ratibida pinnata</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Ratibida_pinnata', '-', 3, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Ratibida_pinnata', '-', 3, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Ratibida_pinnata', '-', 3, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Ratibida_pinnata', '-', 3, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

:::: {.column .species-even width='98%'}

<center>Silphium lacinatum</center>

::: {.column .species-number width='49%'}

<center>Realized</center>
```{r}
sd_question('numeric', paste0('Silphium_lacinatum', '-', 3, '-realized-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Silphium_lacinatum', '-', 3, '-realized-prop'), 'Proportion of Seedmix?')
```

:::

::: {.column .species-number width='49%'}
<center>Desired</center>
```{r}
sd_question('numeric', paste0('Silphium_lacinatum', '-', 3, '-desired-area'), 'Proportion of Area?')
sd_question('numeric', paste0('Silphium_lacinatum', '-', 3, '-desired-prop'), 'Proportion of Seedmix?')
```

:::

::::

```{r}
sd_next(next_page = 'end', label = 'Head to exit')
```

:::


::: {#end .sd-page}
 
## End
 
Thanks for your help, we know the data are a little nebulous, but it is difficult to balance responses with survey length.
 
```{r}
sd_close('Exit Survey')
```
 
:::
