---
echo: false
warning: false
---

```{r}
library(surveydown)
```

::: {#welcome .sd-page}

# Welcome to our survey!

This is a simple demonstration of a surveydown survey. It has two pages with one question on each page.

Here is a basic "multiple choice" question, created using `type = 'mc'` inside the `sd_question()` function:

```{r}
sd_question(
  type  = 'mc',
  id    = 'penguins',
  label = "Which type of penguin do you like the best?",
  option = c(
    'Adélie'    = 'adelie',
    'Chinstrap' = 'chinstrap',
    'Gentoo'    = 'gentoo'
  )
)
```

You need to insert next buttons with `sd_next()` and set the `next_page` argument to the name of the page you want to go to next.

```{r}
sd_next(next_page = 'page2')
```

:::

::: {#page2 .sd-page}

This is another page in your survey.

{surveydown} supports many types of questions. For example, here is a simple `text` type question:

```{r}
sd_question(
  type  = "text",
  id    = "silly_word",
  label = "Write a silly word here:"
)
```

```{r}
sd_next(next_page = 'page3')
```

:::


::: {#page3 .sd-page}
### Region XX - Alaska

In NLCD XX - DWARF SHRUBS how often do you use the following lifeforms in restoration? 
```{r Matrix for Lifeforms}
#| column: screen-inset-shaded
#| layout-nrow: 4
#| layout-ncol: 1
sd_question(
  type  = "numeric",
  id    = "Graminoid12-area",
  label = "Graminoids:"
)
sd_question(
  type  = "text",
  id    = "Forbs12-area",
  label = "Forbs:"
)
sd_question(
  type  = "text",
  id    = "Shrubs12-area",
  label = "Shrubs:"
)
sd_question(
  type  = "text",
  id    = "Trees12-area",
  label = "Trees:"
)
```

```{r}
sd_next(next_page = 'end')
```

:::


::: {#end .sd-page}

## End

This it the last page in the survey.

```{r}
sd_close("Exit Survey")
```

:::
