---
title: "Estimating Seed Market Size in the US"
subtitle: "from Lifeforms to Species"
author: "Reed Clark Benkendorf"
date: "2024-December-13"
institute: "Chicago Botanic Garden"
date-format: long
format: 
  revealjs:
    theme: black
    highlight: pygments
    preview-links: auto
    logo: ./images/CBG_Logos/NegauneeInstitute_CBG-Logo-FlowerMark.png
    chalkboard: 
      boardmarker-width: 5
    reveal_options:
      width: 1920
      height: 1080
      fontsize: 20pt
css: styles.css
editor: 
  markdown: 
    wrap: 72
include-in-header:
  - text: |
      <style>
      #title-slide .title {
        font-size: 1.5em;
      }
      </style>
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, comment = "")
```

```{r Load Libraries}
library(sf)
library(tidyverse)
library(ReDaMoR)
```

```{r Mid term model data}

s <- seq(0.1, 25, by = 0.1)
p <- seq(0, 1, length=100)

bs_visual <- data.frame(
  Theme = c(
    rep('Land Cover', length(s)*2),
    rep('Application', length(p)*2),
    rep('Seed Mixes', length(p)*2), 
    rep('Constants', length(s))
    ),
  Variable = c(
    rep('NLCD Class', length(s)),
    rep('Class-Slope', length(s)),
    rep('Restoration\nMethod', length(p)), 
    rep('Seeding Rate',  length(p)), 
    rep('Prop.\nSeed Mixes',  length(p)), 
    rep('Prop. in Mix', length(p)), 
    rep('PLS/lb',  length(s)) 
),
  x = c(
    rep(s, times = 2), 
    rep(p, times = 4),
    s
    ), 
  y = c(
    dnorm(s, mean = 12.5, sd = 5), 
    dnorm(s, mean = 12.5, sd = 2.5), 
    dbeta(p, 4, 9), 
    dbeta(p, 2, 20), 
    dbeta(p, 5, 2), 
    dbeta(p, 2, 3), 
    dchisq(s, df = 6)
  )
) |>
  mutate(
    Variable = factor(
      Variable, levels = c('NLCD Class', 'Class-Slope', 'Restoration\nMethod', 'Seeding Rate', 'Prop.\nSeed Mixes', 'Prop. in Mix', 'PLS/lb'))
  )

rm(s, p)
```

# Introduction 

## National Seed Strategy Keystone Initiative - Action Plan  

[Action 4. Enhance coordination (within DOI and across departments) to improve the native seed supply chain]{style="color:#6c6c6c; font-size: 0.8em;"}  

- [Short-term (implementation within 1st year of Action Plan)]{style="color:#6c6c6c;"}  
  - **Develop seed need projections for DOI agencies**  
  
- [Mid-term (implementation in 1-3 years of Action Plan)]{style="color:#6c6c6c;"}  
  - **Develop seed need projections for DOI agencies for one-, five-, and ten-year timeframes using NISRC national, central coordinating data platform** (see Action #1)  
  
::: notes
The Keystone plan has three objectives related to estimating the seed needs. Above I have reproduced 2 of the three, the third which is not represented - has a longer time frame for implementation. But should draw heavily from the Mid-Term estimates. 
:::

## historic seed purchase data  

::: {.incremental}
- Data were collected in times when seed availability is low.  
- The right seed, was the available seed   
- Geographically restricted to a few of the 12 DOI regions, and agencies  
- Unable to provide information on *wants* or *needs*  
<br>
- **All data are contextual -  NSRIC is a paradigm shift. **  
:::

::: notes 
While data exists on what BLM purchased and when, the purchasing is shaped largely by availability of seed. As we know the market leaves much to be desired, basing our estimates on low performance purchases will predict a low performance market. 
Further much of these data are restricted to just a handful of regions and agencies relative to the DOI's domain. 
:::

## hesitations of farmers and investors  

::: {.incremental}
- Little knowledge of native species behavior in cultivation  
- Little support from agricultural extensions  
- They are betting on the market  
- Market suffers in low fires years  
- ... 
:::

::: notes
Yes, obviously farmers need more information on *how* to grow the seed, and get it to market. They understand that the value of seed varies in time, however the value of many commodities vary in time - even subsidized staples like corn and soy. If we can better predict the amount of seed which the gov't can purchase and warehouse at points in time, we can decrease the variation in cost and bring it *more* in line like many other crops 
:::

## ~~hesitations of~~ farmers and investors

::: {.vcenter}
::: {.fragment}
> *"There's gold in them thar hills"*  
:::
:::

<br> 

::: {.fragment} 
<center>
Price of an ounce of gold from 1843-1856 - $20.67^1^
</center>
:::

<br>
<br> 

::: {.fragment} 
::: {style="color:#6c6c6c; font-size: 0.8em; text-align: right"}  
^1^[Onlygold.com](https://onlygold.com/gold-prices/historical-gold-prices/)
:::
:::

::: notes
However, this is a country of boom and bust. Most of the West was founded by people looking for fortunes, and I think the possibilities of financial gains outweigh the restrictions that are imposed by a lack of knowledge of the crops. 
:::

# a framework for estimating seed need  

- Domain   
  - DOI Regions (12) 
  - Each DOI Agency (3/4?)  
- Temporal Grain: Annual  
- Spatial Grain: 30m  
- Data Sources: 

::: notes
Ideally we could estimate the demand for native seeds for the next 3-7 years reliably. This would allow for a crop to be purpose grown, e.g. for an anticipated wildfire of a certain size. 
However, It is likely to be some time before we can properly estimate the amount of area which will experience a disaster at X point in time in Y space.  

But when we do get there, we are going to need most of the same variables which we need to start gathering now. Accordingly we can begin our estimates of seed market need at both the short and mid term time points, and later incorporate these data into a long term model. 
::: 

## modelling framework - long term   

## modelling framework - short term 

- Four lifeforms: 
  Grasses, Forbs, Shrubs, Trees  

<font size ="4">
$$
\text{Burned Area} * \text{Seeding Method}* \frac{\text{Pure Live Seed}}{\text{Area}} = \text{PLS required}
$$
</font>

## short term - snapshot 

## modelling framework - mid term 

<font size='4'>
<details> 
<summary>Model</summary>
$$
\text{Cover Class} * \text{Slope Category} * \text{Restoration Type} * \text{Seeding Rate} * \text{Prop. Seed Mixes} * \text{Prop. of Mix} * \text{PLS/lb}
$$
</details>

<details>
<summary>Data Sources</summary>
$$
\frac{\text{Cover Class} * \text{Slope Category}}{\text{Landscape}} * \frac{\text{Restoration Type} * \text{Seeding Rate} * \text{Prop. Seed Mixes} * \text{Prop. of Mix}}{\text{Practicioner Knowledge}} * \frac{\text{PLS/lb}}{\text{NRCS}}
$$
</summary>
</details>

<details> 
<summary>Model Details</summary>
<center>
```{r Mid term model visual view, fig.width=5, fig.height=1}
ggplot(data = bs_visual, aes(x = x, y = y)) + 
  geom_line() + 
  geom_area(fill = 'white') + 
  facet_wrap(~Variable, scales = 'free', nrow = 1) + 
  theme_void() + 
  theme(
    strip.text = element_text(color = 'white'),
    aspect.ratio = 1/1, 
    panel.spacing = unit(0, 'points'), 
    panel.background = element_rect(fill='#191919'), 
    plot.background = element_rect(fill='#191919', color=NA)
    )
```
</center>
</details>

<details> 
<summary>Example</summary>
<center>
"How much [Elymus elymoides]{style="text-decoration: underline;"} *(species)* is required on BLM land in DOI region 10 *(domain)* next year *(grain)*?"

```{r Mid term modelling visualized}
DiagrammeR::grViz("digraph{
 
      graph[rankdir = LR]
      bgcolor = black
      node[shape = rectangle, style = filled]
      
      subgraph cluster_0 { 
         graph[shape = rectangle]
         style = rounded
         bgcolor = '#755C1B'
    
         label = 'Cover Class\n(Area)'
         node[shape = rectangle, fillcolor = '#B78F2A', margin = 0.25]
         A[label = 'NLCD 52 Shrub Scrub']
         Aa[label = 'NLCD 82 Grassland']
        }
      
      subgraph cluster_1 {
         graph[shape = rectangle]
         style = rounded
         bgcolor = '#83BCA9'
    
         label = 'Cover Class x Slope\n(Area)'
         node[shape = rectangle, fillcolor = '#A2CDBF', margin = 0.25]
         C[label = 'NLCD 52 > 10%']
         D[label = 'NLCD 52 < 10%']
      }
      
      subgraph cluster_2 {
         graph[shape = rectangle]
         style = rounded
         bgcolor = '#83BCA9'
    
         label = 'Cover Class x Slope\n(Area)'
         node[shape = rectangle, fillcolor = '#A2CDBF', margin = 0.25]
         Cc[label = 'NLCD 82 > 10%']
         Dd[label = 'NLCD 82 < 10%']
      }        
        
      subgraph cluster_3 {
         graph[shape = rectangle]
         style = rounded
         bgcolor = '#F76F8E'
    
         label = 'Restoration Method\n(Area)'
         node[shape = rectangle, fillcolor = '#F99FB4', margin = 0.25]
         E[label = 'Drill']
         F[label = 'Aerial']
         G[label = 'Hydro']
         H[label = 'Broadcast']
      } 
      
      subgraph cluster_4 {
         graph[shape = rectangle]
         style = rounded
         bgcolor = '#F76F8E'
    
         label = 'Restoration Method\n(Area)'
         node[shape = rectangle, fillcolor = '#F99FB4', margin = 0.25]
         Ee[label = 'Drill']
         Ff[label = 'Aerial']
         Gg[label = 'Hydro']
         Hh[label = 'Broadcast']
      } 
      
      subgraph cluster_5 {
         graph[shape = rectangle]
         style = rounded
         bgcolor = '#5E5C6C'
    
         label = 'Seeding Rate\n(Count)'
         node[shape = rectangle, fillcolor = '#7D7B8E', margin = 0.25]
         I[label = 'seeds/area']
         J[label = 'seeds/area']
         K[label = 'seeds/area']
         L[label = 'seeds/area']
      } 
      
      node[fillcolor = '#0B5563', margin = 0.2]
      M[label = 'Prop. Area Applied to']
      
      node[fillcolor = '#89023E', margin = 0.2]
      N[label = 'Prop. of Seed Mix\n(when Used)']
      
      edge[color = white, arrowhead = vee, arrowsize = 1.25, linesize = 2.5]
      A -> {C D}
      Aa -> {Cc Dd}
      C -> {E F G H}
      D -> {Ee Ff Gg Hh}
      E -> I
      F -> J
      G -> K
      H -> L
      {I J K L} -> {M}
      M -> N
      
      }", width = 1000, height = 400)
```
</center>
</details>
</font>

## modelling framework - long term  

## a framework for associating costs with seed need  

## modelling framework what do we need to achieve mid-term estimates?   

# Proposal 

Three additional elements are required to achieve the modelling goals. 

## a survey of the experts I  

The US federal land management agencies have a plurality of the worlds restoration expertise... unstructured... 

:::: {.columns}
::: {.column width = '50%'}
::: {.fragment}
::: {.incremental}
- biggest concern: completion 
  - minimize the number of questions each participant sees  
- Estimate based survey
  - allows faster completion, less do-not-finish respondents  
  
:::
:::
::: 

::: {.column width = '50%'}
::: {.fragment}
::: {.incremental}
- Survey using R Shiny  
  - supports 'dependencies' within survey's 
  - Sends respondents from different regions and organizations different sets of questions  
- Anticipated [cost: \$49 or \$98](https://www.shinyapps.io/)

:::
::: 
:::
:::: 

## a survey of the experts II 

```{r}
install.packages("surveydown")
```

## survey - short term I 

```{r Relational Data Model for Survey Results - Short Term,  fig.width=5, fig.height = 5}
sh_dm_plot <- readRDS('./images/ShortTermERD.rda')
sh_dm_plot
#htmltools::HTML(DiagrammeRsvg::export_svg(sh_dm_plot))
rm(sh_dm_plot)
```

## survey - medium term II
<center>
```{r Relational Data Model for Survey Results - Medium Term, fig.width=10, fig.height = 3.5}
mt_dm_plot <- readRDS('./images/MediumTermERD.rda')
mt_dm_plot
#htmltools::HTML(DiagrammeRsvg::export_svg(mt_dm_plot))
rm(mt_dm_plot)
```

</center> 

## a survey IV - medium term 

- An R.C. and Nancy adventure  

## an R package for seed need estimates   

<br>

> "the fundamental unit of **distributable** code in the R programming language" 

[*Open, Reproducible, and Distributable Research With R Packages* Josh Brinks]{style="color:#6c6c6c; font-size: 0.8em; text-align: right"} 

::: {.incremental}
- Reproducible  
- Avoids duplication of efforts 
- Testable across Operating Systems (OS)  
- Allows others to engage with problems at their 'head'   
:::

::: notes
Theoretically most of our values and work should be transferrable to other municipal governments, as well as companies interested in producting seed. 
Futher there is one very large DOI agency - the BIA - which I think may not be the most involved in this process, and it seems similar processes will need to be done in Puerto Rico, and the Pacific Islands may very well just more or less redo much of this themselves. 
So it would be great to be able to get folks onto the same playing field without much effort. 

In the botany community sharing 'scripts' seems common, which yes we can do, but most important is actually developing code of the quality that it can be bound into packages and the functions can be shared. This allows us to ensure that the analyses are actually reproducible, and that the code works on multiple operating systems. 

Forest service has for a long time loosely followed this tradition, although lot's of their software is in external programs making maintenance very hard. Both the USGS and EPA are frequent developers of R packages for various analysis. 
::: 


## Timeline  

```{r Timeline plot, fig.width=16, fig.height=9}
months <- data.frame( # these are the center bar. 
  X = c(1, 32, 60, 91, 121, 152, 182, 213, 244, 274, 305, 335),
  Y = 90,
  Month = month.abb
)

people <- data.frame(
  Person = c('Nancy', 'R.C.', 'Becky', 'Ryan', 'Rebecca'),
  X = 0, 
  Y = seq(40, 5, by = -8)
)


people_help <- data.frame(
  Person = rep(c('Nancy', 'R.C.', 'Becky', 'Ryan',  'Rebecca'), each = 2),
  X = c(32, 73, 32, 73, 15, 40, 174, 227, 161, 175),
  Y = rep(seq(40, 5, by = -8), each = 2)
  ) |>
  sf::st_as_sf(coords = c('X', 'Y')) |>
  dplyr::group_by(Person) |>
  summarize(geometry = sf::st_union(geometry)) |>
  sf::st_cast('MULTILINESTRING') |>
  sf::st_buffer(0.5)

milestones <- data.frame(
  Milestone_l = 
    c('Survey', 'Short-term\nestimates', 'R package', 
      'Mid-term\nestimates\n(internal)', 'Mid-term\nestimates'), 
  Milestone = 
    c('Survey', 'Short-term', 'R_package', 'Mid-term_internal', 'Mid-term'),
  X = c(74, 122, 182, 228, 274), 
  Y = c(rep(200, 3), 197.5, 200)
)

## just buffer the circles by how long the event takes... 

# buffer amount will define the date range eaten up by each circle. 
# buffer 1 = 1 week, 2 = 2 weeks, buffer 4 = 4 weeks
circles <- data.frame(
  Event = c(
    'Survey Research', 'Survey Development', 'Survey Release',
    'Lifeform tabulation', 'Analysis', 'Reporting', 
    'Assemble', 'Test', 'Document', 
    'Analyse', 'Troubleshoot', 'Share', 
    'Analyse', 'Style', 'Report'
    ), 
  Milestone = 
    rep(c('Survey', 'Short-term', 'R_package', 'Mid-term_internal', 'Mid-term'), each = 3),
  X = c(
    8, 35, 73, 
    87, 105, 113, 
    140, 159, 174, 
    187, 200, 214, 
    233, 259, 273 
    ), 
  Y = 90,
  buffer = c(
    2, 3.5, 2.5, 
    1, 2, 1,
    4, 2, 1.5,
    3, 1, 1, 
    3.5, 2, 1
    ) * 7
) |>
  sf::st_as_sf(coords = c('X', 'Y'))

belt <- data.frame(
  X = c(0, 365), 
  Y = 90
) |>
  sf::st_as_sf(coords = c('X', 'Y')) |>
  sf::st_union() |>
  sf::st_cast('LINESTRING') |>
  sf::st_buffer(3.5)

circles <- split(circles, f = 1:nrow(circles)) |>
  lapply( FUN = function(x){dist <- jitter(x$buffer, amount = 5); x <- sf::st_buffer(x, dist)}) |>
  bind_rows() |> 
  arrange(-buffer)

explanations <- data.frame(
  explanation_l = c(
    "Research, Develop, & Release\na 15-20 minute survey\nfor land managers from the\nDOI agencies using Shiny", 
    "Tabulate, Analyse, & Report\n estimates of seed\nneeds by lifeforms", 
    "Develop, Test, & Document\na stable version of\n`rseedneed` to github", 
    "Analyse, Troubleshoot & Share\nestimates of mid-term\nseed requirements,\nand distribute internally.", 
    "Analyse, Style, & Report\n feedback from previous\niteration to prepare results\nfor distribution."
  ), 
  Milestone = c('Survey', 'Short-term', 'R_package', 'Mid-term_internal', 'Mid-term'), 
  X = c(74, 122, 182, 228, 274)-10, 
  Y = 155 + rep(c(12, -12), times = 3)[1:5]
)

# lines for each persons contributions

pal <- c('#755C1B', '#83BCA9', '#F76F8E', '#5E5C6C', '#0B5563')
names(pal) <- explanations$Milestone

ggplot() +  
  geom_sf(data = people_help) + 
  geom_sf(
    data = circles, alpha = 0.5, 
    aes(fill = Milestone)) + 
  geom_sf(
    data = belt, fill = '#191919', color = NA, alpha = 0.6) + 
  geom_text(
    data = months,
    aes(x = X, y = Y, label = Month), 
    color ='white', size = 5) + 
  geom_text(
    data = people, 
    aes(x = X, y = Y, label = Person), 
    color ='grey80', size = 4.75) + 
  geom_label(
    data = milestones, 
    aes(x = X, y = Y, label = Milestone_l, fill = Milestone), 
    color ='white', label.size = NA, size = 6) + 
  geom_label(
    data = explanations,
    aes(x = X, y = Y, label = explanation_l, fill = Milestone),
    alpha = 0.2, size = 4.5, color ='grey90', label.size = NA) + 
  scale_fill_manual(values = pal) + 
  theme_void() + 
  ylim(0, 205) + 
  xlim(0, 366) + 
  theme(
    legend.position = 'none',
    panel.background = element_rect(fill='#191919'), 
    plot.background = element_rect(fill='#191919', color=NA)
    )


rm(belt, circles, explanations, milestones, months, people, people_help)
```



