---
echo: false
warning: false
format:
  html:
    theme: [flatly, styles.css]
    grid: 
      sidebar-width: 100px
      margin-width: 100px
barposition: top 
---

```{r}
library(surveydown)
region <- 12
nlcd <- c(42, 52, 68)
```

::: {#welcome .sd-page}

# Welcome to our survey!

We would like to know a little bit about you so that we only ask questions relevant to your expertise.  

```{r respondent name}
sd_question(
  type  = "text",
  id    = "FirstName",
  label = "What is your first name?"
)

sd_question(
  type  = "text",
  id    = "LastName",
  label = "And your last name?"
)

```

```{r}
sd_next(next_page = 'species')
```

:::

:::: {#species .sd-page} 
### Species 

#### What percent area in each NLCD is this species applied? 

```{r Species By Area}
#| column: screen-inset-shaded
#| layout-ncol: 3
#| layout-nrow: 2

sd_question("numeric", id = paste0("Graminoid", region, '-', nlcd[1], "area"),  label = paste0(nlcd[1], " Current"))
sd_question("numeric", id = paste0("Graminoid", region, '-', nlcd[2], "area"), label = paste0(nlcd[2], " Current:"))
sd_question("numeric", id = paste0("Graminoid", region, '-', nlcd[3], "area"), label = paste0(nlcd[3], " Current:"))

sd_question(type  = "numeric", id = paste0("Forbs", region, '-', nlcd[1], "area"), label = "Forbs:")
sd_question(type  = "numeric", id = paste0("Forbs", region, '-', nlcd[2], "area"), label = "Forbs:")
sd_question(type  = "numeric", id = paste0("Forbs", region, '-', nlcd[3], "area"), label = "Forbs:")
```

#### When used, what percent of a seed mix does it constitute?  

```{r Species by Seed Mix}
#| column: screen-inset-shaded
#| layout-ncol: 3
#| layout-nrow: 2
#| 
sd_question(type  = "numeric", id = paste0("Shrubs", region, '-', nlcd[1], "area"), label = "Shrubs:")
sd_question(type  = "numeric", id = paste0("Shrubs", region, '-', nlcd[2], "area"), label = "Shrubs:")
sd_question(type  = "numeric", id = paste0("Shrubs", region, '-', nlcd[3], "area"), label = "Shrubs:")

sd_question(type  = "numeric", id = paste0("Trees", region, '-', nlcd[1], "area"), label = "Trees:")
sd_question(type  = "numeric", id = paste0("Trees", region, '-', nlcd[2], "area"), label = "Trees:")
sd_question(type  = "numeric", id = paste0("Trees", region, '-', nlcd[3], "area"), label = "Trees:")
```

```{r}
sd_next(next_page = 'Alaska_species')
```

::::

::::: {#Alaska_species .sd-page} 

### Region 11 - Alaska - Species 

When species the species is the EC to the SPP

:::: {.column .species-odd width="98%"} 

<center>SPECIES 1 NAME GOES HERE.</center>   

::: {.column .species-numbers width="49%"} 

<center>Realized</center>
```{r}
sd_question(type  = "numeric", id = paste0("Trees", region, '-', nlcd[1], "area"), label = "Proportion of Area?")
sd_question(type  = "numeric", id = paste0("Trees", region, '-', nlcd[1], "area"), label = "Proportion of Seedmix?")
```

:::

::: {.column .species-numbers width="49%"} 

<center>Desired</center>
```{r}
sd_question(type  = "numeric", id = paste0("Trees", region, '-', nlcd[1], "area"), label = "Proportion of Area?")
sd_question(type  = "numeric", id = paste0("Trees", region, '-', nlcd[1], "area"), label = "Proportion of Seedmix?")
```

:::

::::

:::: {.column .species-even width="98%"} 

<center>SPECIES 2 NAME7  </center>

::: {.column .species-numbers width="49%"} 

<center>Realized</center>
```{r}
sd_question(type  = "numeric", id = paste0("SPP-realized", region, '-', nlcd[1], "area"), label = "Proportion of Area?")
sd_question(type  = "numeric", id = paste0("SPP-realized", region, '-', nlcd[1], "area"), label = "Proportion of Seedmix?")
```

:::

::: {.column .species-numbers width="49%"} 

<center>Desired</center>  
```{r}
sd_question(type  = "numeric", id = paste0("SPP-desired", region, '-', nlcd[1], "area"), label = "Proportion of Area?")
sd_question(type  = "numeric", id = paste0("SPP-desired", region, '-', nlcd[1], "area"), label = "Proportion of Seedmix?")
```

:::

::::

:::::


