---
title: "Extreme Fire Values"
author: "Reed Benkendorf"
date: "2024-12-20"
output: html_document
---

```{r}
library(tidyverse)
library(extRemes)
source('functions.R')
```

```{r Import Fire data}
annual <- read.csv('../data/processed/NoFires-TotalArea_byDOIRegion.csv')
```

Both the frequency and size of very large fires appears to be increasing over time, as illustrated by plots made in the SCRIPT NAME. 
These expectations are aligned with our both our experience of working in public lands for over a decade, and reports by the media. 
Because a clear trend is present with these very large fires we will treat this process as *non-stationary*. 

I am most interested in the total amount of area burned in a region each year, and the number of very large fires within that area. 
While the size of fires vary within a season, with the largest fires often burning in late summer and needing to be naturally extinguished by fall temperatures, we will not analyze data at the within season scale.
We will treat the sum of all areas as a a yearly block maxima for these purposes. 

While non-stationary data are more commonly used with the GP distribution, the GEV distribution is more generally used for block maxima. 
We will use the GEV distribution, because GP does not lend itself to single annual values. 


```{r Calculate Fire Return Intervals}
regs <- split(annual, f = annual$REG_NAME)
lapply(regs, CalculateReturnIntervals)

png_files <- list.files(
  '../results/Plots/FireReturnIntervals', 
  pattern = ".*png$", full.names = TRUE
  )

gifski::gifski(
  png_files, 
  gif_file = '~/Documents/assoRted/SeedMarketSizingTalk/images/FireReturnInterval.gif', 
  width = 800, height = 600, delay = 2)
```

