---
title: "Simulate Fire Growth"
author: "Reed Benkendorf"
date: "2025-03-25"
output: html_document
---

A main goal of the simulations is to determine not only how much area may burn, but also *which* areas may burn.
In particular, the NLCD classes of the aresa which may burn, which can be used to crosswalk the total burned area back to seed mixes. 
By combining the total areas to burn, with wildfire probability burn surfaces from the US Forest Services Missoula Fire Lab, we can come up with some decent scenarios. 

Here we develop a function which reflects a process for combining these data. 

The original design of the function follows just a couple simple steps, and iterates on a subset of them. 

1) Using the Pr. Wildfire surface, performs a weighted sample **X** points. 
2) Extracts points in three equidistant rings around the focal point. 
3) Using the mean Pr. wildfire surface score for all points, assigns a possible fire size to this ignition source. 
4) Assigns the raster cells bordering the ignition source to 'burned' (NA), if the total fire area will be 1000 acres (and raster cells are 1 acre each), the closest 200 cells are considered the initial burn. 
5) **Iteration begins here.** Identify all cells adjacent to the current burn, and using weighted sampling, sample 50% of them and assign them as burned. 
6) To 50% of these newly marked cells, assign all of their queen neighbors to burned. 


```{r}
bp <- file.path('..', 'data', 'geospatial', 'WildfireProbability')
ras <- terra::rast( file.path(bp, 'I_FSim_CONUS_LF2020_270m', 'CONUS_BP.tif'))

# devtools::install_github("jolars/euclidr")

SimFireGrowth <- function(n, dists, samps){
  
  
  ### prep work. all simulations will use these base products 

  
  # load relevant raster for the area of interest
  
  # mask raster to DOI region under analysis (for CONUS only)
  
  ### now enter a set of simulations for a single 5 year trajectory in an area. 
  # this is important because we will keep masking the areas which can burn. 
  
  
  # Sample cells from raster using Pr. wildfire weights 
  # this is our method for putting fires in areas where fires mostly make sense. 
  ignition <- terra::spatSample(ras, size = n, method = 'weights', xy = TRUE) |>
    sf::st_as_sf(coords = c('x', 'y'), crs = terra::crs(ras))
  
  # now add the equidistant rings to each ignition point, we will extract these
  # values and use them to sample to determine plausible total fire size matches

  # do this through every single ignition point. 
  igL <- split(ignition, f = 1:nrow(ignition))
  
  boyo <- lapply(
    igL, function(x){
      
        ringPts2 <- Map(ringPts, rep(igL, times = length(dists)),  dists, samps) |>
          dplyr::bind_rows() |>
          sf::st_transform(terra::crs(ras))

        ob <- mean(terra::extract(ras, ringPts2, na.rm = TRUE, ID = F)[[1]])
          
    }) |> as.numeric()
  
  # assign a total fire size to the points based on their surroundings. 
  
  # 'burn in' an initial 20% of the total fire size around the ignition point. 
  
  # this will require calculating distances, we will restrict calculations to a distance
  # which is equal to 
  
}

pt <- data.frame(x = -88.720, y = 42.179) |>
  sf::st_as_sf(coords = c('x', 'y'), crs = 4326)
pt_planar <- sf::st_transform(pt, 5070)

ob <- SimFireGrowth(n = 10, dists = c(1e3, 5e3, 1e4), samps = c(8, 24, 48))



order(ob)

# the max distance we will search is for a fire which grows as a rectangle with 
# dimensions 1:5
totalArea = 100
hyp <- sqrt(((2.5^2) + ((totalArea/5)/2)^2))

plot(density(ob))

```



```{r}
#' sample points at ring distances for calculating wildfire environment. 
#' @param x the center point
#' @param dists the distance to work out from this point
#' @param samps the number of points to return from the ring. Going above 50 drastically increase compute time. 
ringPts <- function(x, dists, samps){
  
  r <- sf::st_cast(
    sf::st_cast(
      sf::st_buffer(x, d),
      'LINESTRING', warn = FALSE),
    'POINT', warn = FALSE
    )
  r <- sf::st_coordinates(r)
  indx <- euclidr:: farthest_points(r, samps)
  
  r <- r[indx,] |>
    data.frame() |>
    sf::st_as_sf(coords = c('X', 'Y'), crs = 5070)
  return(r)
}


```

