---
title: "Tabulate Terrestrial Areas by DOI Region"
author: "Reed Clark Benkendorf"
date: "2025-01-27"
output: pdf_document
---

To estimate the amount of native seed required by each Department of Interior (DOI) region via the simulations several constants are required. 
These constants largely reflect the amount of terrestrial area per DOI region, and how these surfaces are allocated between administrative agencies. 
These calculations are performed in this document these values are then utilized for all subsequent analyses and products. 

Here we calculate the following values,
1) The sum of terrestrial area administered by each DOI agency
2) The sum of terrestrial area administered in each DOI region  
3) The sum of terrestrial area administered by each DOI agency in each DOI region 
4) The sum of National Land Cover Data (NLCD) classes, on DOI agency administered land by DOI region
5) The sum of NLCD classes by each DOI agency by DOI region

```{r load libraries}
library(tidyverse)
library(terra)
library(sf)
```

# 1, 2, & 3 Total sums of terrestrial area managed by DOI agencies

```{r Import DOI regions data}
p <- file.path('..', 'data', 'geospatial', 'AdministrativeUnits', 'DOIRegions', 'DOI_12_Unified_Regions_20180801.shp')
regions <- st_read(file.path(p), quiet = TRUE) |>
  sf::st_transform(4326) |>
  sf::st_make_valid()
```

The sum of terrestrial area administered by each DOI agency can be calculated by simply summing over the entire PADUS data set, which we have subset to the relevant agencies. 

```{r import terrestrial management surfaces data}
p <- file.path('..', 'data', 'geospatial', 'DOIadministered')
padus_geo <- st_read(file.path(p, 'DOIterrestrial-geographic.gpkg'), quiet = TRUE) 
padus_plan <- st_read(file.path(p, 'DOIterrestrial.gpkg'), quiet = TRUE)
rm(p)
```

A difference exists between the true total area managed by each agency, and the amount of mapped GIS acres for each agency. 
It appears Protected Areas Database of the United States (PADUS) version 4 has around 98-99% of all areas mapped, mapping areas is a long process and has not been completed for all parcels yet. 
We have confirmed that our calculations match the PADUS teams GIS acres calculations precisely, and have ruled out all other sources of error. 
Note that we have also removed very large bodies of water, and some totally barrn playas from the area estimates, hence each agency comes in 'beneath' their official estimates of GIS acres as well. 

```{r calculate total terrestrial area managed by each agency}

Areas <- data.frame(
  Mang_Name = padus_geo$Mang_Name,
  Geographic = as.numeric(units::set_units(st_area(padus_geo), ha)),
  Planar = as.numeric(units::set_units(st_area(padus_plan), ha))
) 

Areas[,2:3] <- apply(Areas[,2:3], MARGIN = 2, \(x) x* 2.4710538146717)
Areas <- Areas |> 
  group_by(Mang_Name) |>
  summarize(
    Total_g = sum(Geographic),
    Total_p = sum(Planar))

knitr::kable(
  Areas, 
  col.names = c('Agency', 'Area (Geographic)', 'Area (Planar)'),
  digits = 0, 
  format.args = list(big.mark = ',')
  )

# total DOI area, around 410,000,000 (that is million) acres. 
sum(Areas$Total_g)
sum(Areas$Total_p)
```

The amount of land managed by each agency varies considerably. 

```{r create data set of terrestrial land by doi region}
p <- file.path('..', 'data', 'geospatial', 'DOIadministered')
padus_geo_regions <- st_read(file.path(p, 'DOIterrestrial-geographic-Regions.gpkg'), quiet = TRUE) 
padus_geo_regions <- sf::st_make_valid(padus_geo_regions)

padus_planar_regions <- st_read(file.path(p, 'DOIterrestrial-planar-Regions.gpkg'), quiet = TRUE)

areas <- as.numeric(units::set_units(st_area(padus_planar_regions), ha))* 2.4710538146717
all_areas <- padus_planar_regions %>% 
  st_drop_geometry() %>% 
  mutate(AREA_ACRES = areas)

areas <- as.numeric(units::set_units(st_area(padus_geo_regions), ha))* 2.4710538146717
padus_geo_regions <- padus_geo_regions %>% 
  st_drop_geometry() %>% 
  mutate(AREA_ACRES = areas) 
```

```{r area administered in each DOI region}

all_areas <- padus_planar_regions %>% 
  st_drop_geometry() %>% 
  mutate(AREA_ACRES = areas) %>% 
  group_by(REG_NAME) %>% 
  summarize(Total_Area = sum(AREA_ACRES))

padus_geo_regions <- padus_geo_regions %>% 
  group_by(REG_NAME) %>% 
  summarize(Total_Area = sum(AREA_ACRES))

ac_region <- padus_geo_regions$Total_Area

knitr::kable(
  all_areas, 
  col.names = c('Region', 'Area (Planar)', 'Area (Geographic)'),
  digits = 0, 
  format.args = list(big.mark = ',')
  )

```


```{r area by each DOI agency in each DOI region}

```

